---
title: "WeekTwo"
output: html_document
---

## Variation

As homework, you all entered your height and the height of your parents. This week, we'll take a look at the variability in the trait height.

```{r}
library(tidyverse)
heights <- read_csv("data/heights_sorted.csv")
```

Let's try plotting the data:


```{r}
ggplot(heights, mapping = aes(generation, height,  color=generation)) + geom_point()
```

What are your observations about these two distributions? Write down two things you notice:

```
# Answer Here

```

Try plotting the data as a boxplot. 

```{r}
ggplot(heights, mapping = aes(generation, height,  color=generation)) + geom_boxplot()
```

What are the lines on a boxplot? If you calculate the means of your heights and your parents, does this mean reflect what you see on the graph:

```{r}

heights %>% 
group_by(generation) %>% 
summarize(mean_hgt = mean(height))

```


Does this change the way you feel about either of your two observations above?


```
# Answer here

```

By eye, would you say these two groups are different? 


```
Answer here
```

Let's put this to the test. In the study of biology, we can quantify differences between groups using a Chi-Squared test. The Chi-Squared test allows us to tell if two or more groups are really different. It uses the distribution of data points to tell this information. For example, our boxplots overlap a little, but not all the way. Is that overlap significant? A Chi-Square test lets us tell. We can then calculate a P-value. This value tells us, if the groups are actually identical, how likely we would be to observe a difference. If your generation has the same distribution of heights, how likely are we to observe these differences.
```{r}
heights %>% 
group_by(generation) %>% 
ungroup %>%
summarise(pval = chisq.test(height, generation)$p.value)

```
