---
title: "WeekTwo"
output: html_document
---

## Variation

As homework, you all entered your height and the height of your parents. This week, we'll take a look at the variability in the trait height.

```{r}
library(tidyverse)
heights <- read_csv("data/heights_sorted.csv")
```

Let's try plotting the data:


```{r}
ggplot(heights, mapping = aes(generation, height,  color=generation)) + geom_point()
```

What are your observations about these two distributions? Write down two things you notice:

```
# Answer Here

```

Try plotting the data as a boxplot. 

```{r}
ggplot(heights, mapping = aes(generation, height,  color=generation)) + geom_boxplot()
```

What are the lines on a boxplot? If you calculate the means of your heights and your parents, does this mean reflect what you see on the graph:

```{r}

heights %>% 
group_by(generation) %>% 
summarize(mean_hgt = mean(height))

```


Does this change the way you feel about either of your two observations above?


```
# Answer here

```

By eye, would you say these two groups are different? 


```
Answer here
```

Let's put this to the test. In the study of biology, we can quantify differences between groups using a Chi-Squared test. The Chi-Squared test allows us to tell if two or more groups are really different. It uses the distribution of data points to tell this information. For example, our boxplots overlap a little, but not all the way. Is that overlap significant? A Chi-Square test lets us tell. We can then calculate a P-value. This value tells us, if the groups are actually identical, how likely we would be to observe a difference. If your generation has the same distribution of heights, how likely are we to observe these differences.

```{r}
heights %>% 
group_by(generation) %>% 
ungroup %>%
summarise(pval = chisq.test(height, generation)$p.value)

```

By now we should have clearly demonstrated that individual organisms within populations demonstrate considerable variation across a wide variety of traits. Some of these traits are easier to quantify than others, but the point remains that no two individuals are quite alike. What are the implications of variation? Do these varioations have any impact on how an organism interacts with its environment? To get started in thinking about this, you will be observing some stuffed bird specimens and taking note of some important traits and how they vary. 

At the Main Entrance to the Biology Building (now Thelma Ryan Hall), there is a display case with four different birds. Another display case can be found in the same building at the entrance to the vertebrate museum with another four birds. Select three different traits (e.g. body coloration, beak size, etc.) and try to develop 3 sets of hypotheses explaining how the variable traits allow the various bird species to interact with their enviroments in unique ways. For example: Birds with darker feathers (species A, B, and C) are more likely to be found in cooler climates where their dark coloration can absorb more heat.

Please write a one page report detailing your hypotheses.
